Replication materials for Beger, Morgan, Ward, nd

### 2020-11-10 rep_nosmooth/README.Rmd
add a master.R script for replication

---
title: "Modified replication"
output: 
  github_document
always_allow_html: true
---

@@

@@

One of the principal outputs of `setup-model-definitions.R` is this encoding, in `output/model-definitions/model-table.rds`:

>>>>

---
title: "Replication materials for Beger, Morgan, Ward, nd"
output: 
  github_document
always_allow_html: true
---

@@

**tl;dr:** run through `master.R`

@@

One of the principal outputs of `1-setup-model-definitions.R` is this encoding, in `output/model-definitions/model-table.rds`:
